---
title: "Assignment 1"
author: "Xicheng Jiang"
date: "2018/9/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Questions:

1.  How would do the following tasks in R?

a. Generate a numeric sequence x1 that starts from -1.25 and goes to 1.25 in
increments of .01. Then show how you would find the length of x1, its class
and attributes

```{r}
x1=seq(-1.25,1.25,0.01) #generating x1
length(x1) # length of x1
class(x1) # class of x1
attributes(x1) # attributes of x1
```

b. Generate a random sequence x2 of 1000 draws from the standard normal
distribution with the seed for the sequence set to 25.

```{r}
set.seed(25)
x2=rnorm(1000)
```

c. Create a character vector x3 consisting of the names of five of your favorite consumer brands.

```{r}
x3=c("Pepsi","Starbucks","McDonald's","Nestle","RedBull")
class(x3)
```

d. Creat a matrix X4 from x2 consisting of 200 rows and 5 columns.

```{r}
X4=matrix(x2,nr=200,nc=5)

```

e. Creat a data.frame object called datdf in which the first column has the name
dts consisting of dates from 2001-01-01 by month, followed by four columns of
the data in X4 with column names var1, var2, var3, var4.

```{r}

dts=seq(as.Date("2001-01-01"),by="month",length.out=200)
var1=X4[,1]
var2=X4[,2]
var3=X4[,3]
var4=X4[,4]
datdf=data.frame(dts,var1,var2,var3,var4)
```

f. Create a list object myls containing the objects in questions a-e.

```{r}
myls=list(x1,x2,x3,X4,datdf)
```

2.  Additional R questions.

a. How is the function attr() used to add meta-data to an R-object? Give
an example by adding some meta-data of your choosing to the object x3 in
question 1.

```{r}
attr(x3,"type")="brand"
attr(x3,"preference")="favorite"
attributes(x3)
```

b. How would you extract the last ten rows of the matrix X4 in question 1?

```{r}
X4[(nrow(X4)-10):nrow(X4),1:5]

```

c. How would you extract the first column of datdf by its column name?

```{r}
datdf[,"dts"]
```

d. How could you save datdf to disk, remove it from the global environment, and
then load it back into your session?

```{r}
write.csv(datdf,file="datdf.csv")
rm(datdf)
datdf=read.csv("datdf.csv")[,-1]

```

3.  Write a function named matmultiply that takes matrices X and Y and
returns the matrix product. In the function body, how would you include a check
that the inputs are matrices and conformable for matrix multiplication?

```{r}
matmultiply=function(X = X, Y = Y){
  if(class(X)!="matrix"){
    stop("X should be matrix")
  }
  else{
    if(class(Y)!="matrix"){
      stop("Y should be matrix")
    }
    else{
          if(dim(X)[2]!=dim(Y)[1]){
            stop("ncolumn of X does not equal to nrow of Y")
          }
          else{
            ans=matrix(nr=dim(X)[1],nc=dim(Y)[2])
            for(i in 1:dim(X)[1]){
              for(j in 1:dim(Y)[2]){
                sum=0
                for(k in 1:dim(X)[2]){
                  sum = sum + X[i,k]*Y[k,j]
                }
                ans[i,j]=sum
              }
            }
          }
    }
      
  }
  return(ans)
}

```

4. Consider the following model 
    y = β0 + β1x + σε
  where
    ε ∼ N(0, 1)
  and (β0, β1, σ) are parameters. Suppose that you had a value of x given to you, and you also had a matrix (call it) outm with m rows and 3 columns of possible values of the parameters. How could you use Monte Carlo simulation to take outm and x as inputs (and perhaps a third input which is the seed for the simulation) and output a m times 1 matrix of possible values of y. Write a function to do this job.
  
```{r}
# The function has 3 variables
# outm, x as well as the number of seed
simulation = function(outm = outm, x=x, seed=seed){
  set.seed(seed)
  ans = matrix(nr=nrow(outm),nc=1)
  ans[1,1] = outm[1,1]+outm[1,2]*x+outm[1,3]*rnorm(1)
  for(i in 2:nrow(outm)){
    ans[i,1] = outm[i,1]+outm[i,2]*ans[i-1,1]+outm[i,3]*rnorm(1)
  }
  return(ans)  
}
```

