---
title: "final"
author: "Xicheng Jiang, Lea Li, Xingyu Chen"
date: "2018/12/9"
output: html_document
---

First part:
In this part we settle the stocks we gonna include in portfolios and fetch the weekly returns of those stocks from 2014-06-01 to 2018-06-01 from Internet.
```{r}
library(quantmod)
library(xts)
library(m537)
library(m537tools)

symbol = c("AAPL","FORD","IBM","BAC","AMZN",
           "T","GOOG","DAL","AXP","LUV",
           "ACN","CEA","AZZ","GS","MSFT",
           "BA","BIDU","BP","BX","PFG",
           "ALE","CS","ADDYY","APF","UBS",
           "AEP","AI","HTA","ASB","FAF",
           "^gspc")

symbolName = c("AAPL","FORD","IBM","BAC","AMZN",
               "T","GOOG","DAL","AXP","LUV",
               "ACN","CEA","AZZ","GS","MSFT",
               "BA","BIDU","BP","BX","PFG",
               "ALE","CS","ADDYY","APF","UBS",
               "AEP","AI","HTA","ASB","FAF",
               "sp500")

prmdf = getfinwdat(symbols = symbol,
                   symnames = symbolName,
                   from = "2014-06-01",
                   to = "2018-06-01")
```

Second part:
In this part we construct our 6 different portfolios and use SURE model with gaussian error and without intercept to estimate those portfolios.
```{r}
capmfrmls5 = list(prmAAPL~prmsp500-1,
                  prmFORD~prmsp500-1,
                  prmIBM~prmsp500-1,
                  prmBAC~prmsp500-1,
                  prmAMZN~prmsp500-1)

capmfrmls10 = list(prmAAPL~prmsp500-1,
                   prmFORD~prmsp500-1,
                   prmIBM~prmsp500-1,
                   prmBAC~prmsp500-1,
                   prmAMZN~prmsp500-1,
                   prmT~prmsp500-1,
                   prmGOOG~prmsp500-1,
                   prmDAL~prmsp500-1,
                   prmAXP~prmsp500-1,
                   prmLUV~prmsp500-1)

capmfrmls15 = list(prmAAPL~prmsp500-1,
                   prmFORD~prmsp500-1,
                   prmIBM~prmsp500-1,
                   prmBAC~prmsp500-1,
                   prmAMZN~prmsp500-1,
                   prmT~prmsp500-1,
                   prmGOOG~prmsp500-1,
                   prmDAL~prmsp500-1,
                   prmAXP~prmsp500-1,
                   prmLUV~prmsp500-1,
                   prmACN~prmsp500-1,
                   prmCEA~prmsp500-1,
                   prmAZZ~prmsp500-1,
                   prmGS~prmsp500-1,
                   prmMSFT~prmsp500-1)

capmfrmls20 = list(prmAAPL~prmsp500-1,
                   prmFORD~prmsp500-1,
                   prmIBM~prmsp500-1,
                   prmBAC~prmsp500-1,
                   prmAMZN~prmsp500-1,
                   prmT~prmsp500-1,
                   prmGOOG~prmsp500-1,
                   prmDAL~prmsp500-1,
                   prmAXP~prmsp500-1,
                   prmLUV~prmsp500-1,
                   prmACN~prmsp500-1,
                   prmCEA~prmsp500-1,
                   prmAZZ~prmsp500-1,
                   prmGS~prmsp500-1,
                   prmMSFT~prmsp500-1,
                   prmBA~prmsp500-1,
                   prmBIDU~prmsp500-1,
                   prmBP~prmsp500-1,
                   prmBX~prmsp500-1,
                   prmPFG~prmsp500-1)

capmfrmls25 = list(prmAAPL~prmsp500-1,
                   prmFORD~prmsp500-1,
                   prmIBM~prmsp500-1,
                   prmBAC~prmsp500-1,
                   prmAMZN~prmsp500-1,
                   prmT~prmsp500-1,
                   prmGOOG~prmsp500-1,
                   prmDAL~prmsp500-1,
                   prmAXP~prmsp500-1,
                   prmLUV~prmsp500-1,
                   prmACN~prmsp500-1,
                   prmCEA~prmsp500-1,
                   prmAZZ~prmsp500-1,
                   prmGS~prmsp500-1,
                   prmMSFT~prmsp500-1,
                   prmBA~prmsp500-1,
                   prmBIDU~prmsp500-1,
                   prmBP~prmsp500-1,
                   prmBX~prmsp500-1,
                   prmPFG~prmsp500-1,
                   prmALE~prmsp500-1,
                   prmCS~prmsp500-1,
                   prmADDYY~prmsp500-1,
                   prmAPF~prmsp500-1,
                   prmUBS~prmsp500-1)

capmfrmls30 = list(prmAAPL~prmsp500-1,
                   prmFORD~prmsp500-1,
                   prmIBM~prmsp500-1,
                   prmBAC~prmsp500-1,
                   prmAMZN~prmsp500-1,
                   prmT~prmsp500-1,
                   prmGOOG~prmsp500-1,
                   prmDAL~prmsp500-1,
                   prmAXP~prmsp500-1,
                   prmLUV~prmsp500-1,
                   prmACN~prmsp500-1,
                   prmCEA~prmsp500-1,
                   prmAZZ~prmsp500-1,
                   prmGS~prmsp500-1,
                   prmMSFT~prmsp500-1,
                   prmBA~prmsp500-1,
                   prmBIDU~prmsp500-1,
                   prmBP~prmsp500-1,
                   prmBX~prmsp500-1,
                   prmPFG~prmsp500-1,
                   prmALE~prmsp500-1,
                   prmCS~prmsp500-1,
                   prmADDYY~prmsp500-1,
                   prmAPF~prmsp500-1,
                   prmUBS~prmsp500-1,
                   prmAEP~prmsp500-1,
                   prmAI~prmsp500-1,
                   prmHTA~prmsp500-1,
                   prmASB~prmsp500-1,
                   prmFAF~prmsp500-1)
```

Third part:
In this part we calculate the training sample priors for each portfolio, and extract the descriptive data for the 15-stock portfolio especially.
```{r}
priorls5 = trainpriorsureg(modelfrmls = capmfrmls5,
                           data = prmdf,
                           trainpct = .15)

priorls10 = trainpriorsureg(modelfrmls = capmfrmls10,
                            data = prmdf,
                            trainpct = .15)

priorls15 = trainpriorsureg(modelfrmls = capmfrmls15,
                            data = prmdf,
                            trainpct = .15)

beta0 = priorls15[["beta0_"]]
write.csv(beta0) # should also include the path you want to store the file

B0 = priorls15[["B0_"]]
write.csv(B0) ## should also include the path you want to store the file

Rho = priorls15[["rho"]]

Sigma0 = priorls15[["Sigma0_"]]
write.csv(Sigma0) ## should also include the path you want to store the file

priorls20 = trainpriorsureg(modelfrmls = capmfrmls20,
                            data = prmdf,
                            trainpct = .15)

priorls25 = trainpriorsureg(modelfrmls = capmfrmls25,
                            data = prmdf,
                            trainpct = .15)

priorls30 = trainpriorsureg(modelfrmls = capmfrmls30,
                            data = prmdf,
                            trainpct = .15)
```

Fourth part:
In this part we construct an optimal portfolio for each portfolio setting, using the 4-year risk free rate and the geometric average market return as our portfolio target return.
```{r}
marketreturn = 1+prmdf[,31]
geometricmean = exp(mean(log(marketreturn)))-1
portmean = geometricmean

rskfree =getrskfree(from = "2014-06-01",to = "2018-06-01");

capmportls5 = makebayesportfolioaftersureg(portmean = portmean,
                                           modelfrmls = capmfrmls5,
                                           data = prmdf)

capmportls10 = makebayesportfolioaftersureg(portmean = portmean,
                                           modelfrmls = capmfrmls10,
                                           data = prmdf)

capmportls15 = makebayesportfolioaftersureg(portmean = portmean,
                                            modelfrmls = capmfrmls15,
                                            data = prmdf)

capmportls20 = makebayesportfolioaftersureg(portmean = portmean,
                                            modelfrmls = capmfrmls20,
                                            data = prmdf)

capmportls25 = makebayesportfolioaftersureg(portmean = portmean,
                                            modelfrmls = capmfrmls25,
                                            data = prmdf)

capmportls30 = makebayesportfolioaftersureg(portmean = portmean,
                                            modelfrmls = capmfrmls30,
                                            data = prmdf)
```

Fifth part:
In this part we plot a graph of number of stocks in a portfolio and the standard deviation of the portfolio, showing that the diversification theory is correct.
```{r}
options(repos=c(CRAN="https://cran.cnr.berkeley.edu/"))
newpacks = c("tidyverse","quantmod",
             "lubridate","xts",
             "Rcpp",
             "RcppArmadillo",
             "reshape2",
             "RColorBrewer",
             "scales",
             "grid",
             "coda",
             "bayesm",
             "MCMCpack"
)
newpacks1 <- newpacks[!(newpacks %in% installed.packages()[,"Package"])]
if(length(newpacks1)) install.packages(newpacks1,
                                       dependencies = TRUE)

lapply(newpacks,
       library,
       character.only = T)
remove(newpacks, newpacks1)

p = ggplot(data = port,
           mapping = aes(x = numStock,y = std))
p2 = p + geom_point
plot(p2)
```

